\newpage

\addcontentsline{toc}{part}{\bibname}

\begin{thebibliography}{50}

\bibitem{JavaScript_Definitive_guide} David Flanagan. JavaScript: The Definitive Guide (Definitive Guides). O'Reilly. 6ª Edición. 2011.

\bibitem{Good_Parts} Douglas Crockford. JavaScript: The Good Parts: Working with the Shallow Grain of JavaScript. O'Reilly, Yahoo press. 2008.

\bibitem{Patterns} Stoyan Stefanov. JavaScript Patterns. O'Reilly, Yahoo press. 2010.

\bibitem{Patterns} Addy Osmani. Learning JavaScript Design Patterns. O'Reilly. 2012.

\bibitem{High_performance} Nicholas C. Zakas. High Performance JavaScript (Build Faster Web Application Interfaces). O'Reilly, Yahoo press. 2010.

\bibitem{Maintanable_javascript} Nicholas C. Zakas. Maintainable JavaScript. O'Reilly. 2012.

\bibitem{Patterns} Alex MacCaw. JavaScript Web Applications. O'Reilly. 2011.

\bibitem{w3c_html5} EMAC. Standard ECMA-262. ECMAScript® Language Specification. Edición 5.1. 2011. \url{http://www.ecma-international.org/ecma-262/5.1/}. PDF \url{http://www.ecma-international.org/publications/files/ECMA-ST/Ecma-262.pdf}

\bibitem{w3c_html5} W3C. Especificación de HTML5. \url{http://www.w3.org/TR/html5/}

\bibitem{w3c_file_api} W3C. Especificación de File API. \url{http://www.w3.org/TR/FileAPI/}

\bibitem{w3c_canvas} W3C. Especificación de Canvas. \url{http://www.w3.org/TR/2dcontext/}

\bibitem{kineticjs} KineticJS. \url{http://kineticjs.com/}

\bibitem{gruntjs} GruntJS. \url{http://gruntjs.com/}

\bibitem{npm} NPM. \url{https://www.npmjs.org/}

\bibitem{nodejs} NodeJS. \url{http://nodejs.org/}

\bibitem{mocha} Mocha. \url{http://visionmedia.github.io/mocha/}

\bibitem{jsdoc} JsDoc. \url{http://usejsdoc.org/}


\end{thebibliography}

\newpage